OSMAC_Method; Model: `r params$Model_Path`; 

### 2022-09-27 Articles.Rmd
Additionally calculate the Average MSE Y for the existing results

remove(Simulated_Data,Model_1,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)

@@

remove(Simulated_Data,Model_2,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                        All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)

@@

remove(Simulated_Data,Model_3,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                        All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)

@@

remove(Simulated_Data,Model_4,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)

@@

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "SMSE_MI_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggexport(filename = "SMSE_MI_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 16)
```

>>>>

remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE
RS_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(RS_ACC,OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Accuracy",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)

@@

remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE
RS_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(RS_ACC,OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Accuracy",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)

@@

remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE
RS_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,All_ACC)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(RS_ACC,OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Accuracy",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)

@@

remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)

@@

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE
RS_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE",All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Accuracy",All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,RS_ACC)

@@

Identical_ro[Identical_ro$Metric=="Accuracy" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Accuracy")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p5

Identical_ro[Identical_ro$Metric=="Accuracy" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' = 100 and r')))+
  ylab("Accuracy")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(color = "black",face = "bold",size = 12),
        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p6

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "SMSE_MI_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggexport(filename = "SMSE_MI_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "ACCURACY_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "ACCURACY_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 12)
```

### 2022-09-27 Identical_r0/Rmarkdown/Classical/OSMAC_Method.Rmd
Additionally calculate the Average MSE Y for the existing results

remove(Temp_P,Temp_W,Temp_Info)

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
     file = here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC.RData"))
```

@@

@@

```{r Final plots 2,fig.height=7,fig.width=20}
Plot_List<-list()

@@

>>>>

Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
Parameter_Data<-as.matrix(Est_Parameter[,-c(1:3)])
Parameter<-Parameter_Data[1,]

Predict_Logistic_Regression<-function(Parameter)
{
  Estimates<-matrix(Parameter)
  fitted_pi<-LaplacesDemon::invlogit(Full_Data[,-1]%*%Estimates)
  fitted_response<-ifelse(fitted_pi > 0.5,1,0)
  return(1-mean(fitted_response != Full_Data[,1]))
}

Accuracy<-apply(Parameter_Data,1,Predict_Logistic_Regression)
Accuracy_Data<-cbind.data.frame(Est_Parameter[,1:3],Accuracy)
Accuracy_Data<-Accuracy_Data %>% 
  group_by(Model,Type,Subsample_Size) %>%
  summarize(Average_Accuracy=mean(Accuracy))

remove(Temp_P,Temp_W,Temp_Info,Full_Data,Parameter_Data,Parameter,Accuracy)

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
     file = here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC.RData"))
```

@@

Accuracy_Data %>% 
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Average Accuracy")+ggtitle("Average Accuracy")->Plot_List[[6]]

@@

```{r Final plots 2,fig.height=7,fig.width=25}
Plot_List<-list()

@@

Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
Parameter_Data<-as.matrix(Est_Parameter[,-c(1:3)])
Parameter<-Parameter_Data[1,]

fitted_pi<-as.vector(predict.glm(Full_model,newdata = as.data.frame(Simulated_Data$All_Data$Real_Model[,-1])))
fitted_response<-ifelse(fitted_pi > 0.5,1,0)
Full_Accuracy<-1-mean(fitted_response != Simulated_Data$All_Data$Real_Model[,1])

Accuracy_Data %>% 
  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Relative Average Accuracy")+ggtitle("Average Accuracy")->Plot_List[[6]]

ggarrange(plotlist = Plot_List,common.legend = TRUE,nrow=1)
```
